ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-12-09 proposal.tex
Removed refernces to deleted figure

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in \autoref{fig:subFunctionalBlock}. Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem. Some of the systems are multiple output and some are single output as depicted in \autoref{fig:subFunctionalBlock}.

>>>>

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems. Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem. Some of the systems are multiple output and some are single output.
